Flatiron cleaning

### 2021-12-02 Rmd/rdi analysis.Rmd
Update html, re-did tables and more

  # 7.Calculate cycle for each line----
  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
  mutate(#drugname_count_perline = n(),
         drugname_count_perline = case_when(
           str_detect(drugname, "platin|taxel")     ~ n()
         )
           ) %>%  # F0000AD999ABF
  ungroup() %>% 
  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor)) %>% 
  group_by(patientid, linenumber_new) %>% 
  mutate(linestartdate_new = min(episodedate)) %>% 
  mutate(lineenddate_new = max(episodedate)) %>% 
  ungroup()
```

- Code cycle number
```{r cycle coding}
# Code cycle number
therapy_cycle <- therapy_line %>% 
  # filter(str_detect(drugname, "taxel|platin")) %>% # Need to that now for patient who got Bev only once per line F02D8628A5394

  arrange(patientid, episodedate) %>% 
  group_by(patientid, linenumber_new) %>%
  # Need the number of time of the "major" drug is seen in the line
  mutate(cycle_count_perline = min(drugname_count_perline, na.rm = TRUE)) %>%
  mutate(cycle_major_drugname = case_when(
    cycle_count_perline == drugname_count_perline          ~ cycle_drugname,
    TRUE                                                   ~ NA_character_
  )) %>% 
  # select(-drugname_count_perline) %>% 
  group_by(patientid, linenumber_new, cycle_major_drugname) %>%
  mutate(cycle_increment = row_number(cycle_major_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------
  # F01D908A013B7 has more pacli at the end but in the same line

@@

  # group_by(patientid, linenumber_new, cycle_inc) %>%
  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>% 
  arrange(patientid, episodedate, cycle_increment) %>% 
  group_by(patientid, linenumber_new) %>%
  # mutate(cycle_increment = cycle_inc) %>% 
  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
  group_by(patientid, chemotherapy_type, cycle_increment) %>% 
  mutate(is_dose_dense = row_number(cycle_increment),
         is_dose_dense = ifelse(is_dose_dense == 1, 1, NA_real_)) %>% 
  group_by(patientid) %>% 
  mutate(total_cycle_increment = row_number(is_dose_dense)) %>% 
  fill(total_cycle_increment, .direction = "downup") %>% 
  # cycle date
  group_by(patientid, linenumber_new, cycle_increment) %>% 
  mutate(cycle_start_date = min(episodedate)) %>%

@@

  # # CODE FOR SKIPPED CYCLE
  # group_by(patientid, linenumber_new) %>% 
  # mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
  #        cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
  # 
  # # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
  # mutate(n = row_number(drugname)) %>%
  # 
  # mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
  # fill(base_days_between_cycle, .direction = "downup") %>% 
  # mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
  #                                      (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
  # # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
  # group_by(patientid, linenumber_new) %>%
  # mutate(drug_count_perline = n()) %>%
  # mutate(skipped_cycle_indays1 = ifelse(
  #   (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
  # )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
  # # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
  # group_by(patientid) %>% 
  # mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
  # ungroup()
therapy_cycle %>% distinct(patientid) %>% nrow()

@@

```{r target_auc and expected dose}
Treatment <- 
  # Merge with creatinine
  left_join(therapy_cycle, creatinine, by = "patientid") %>%
  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_creat = case_when(
    (therapy == "Upfront Surgery" &
       interval_creat < 31 &
       # creat_date < lineenddate &
       creat_date > surgerydate)                  ~ interval_creat,

@@

```{r plot interval}
Treatment %>% 
  ggplot(aes(x= interval_creat)) +
  geom_bar() #+
  # coord_cartesian(ylim=c(0,50))
# Treatment %>% 
#   ggplot(aes(x= interval_height)) +
#   geom_bar() +
#   coord_cartesian(ylim=c(0,50))
Treatment %>% 
  ggplot(aes(x= interval_weight)) +
  geom_bar() #+
  # coord_cartesian(ylim=c(0,50))
Treatment %>% 
  ggplot(aes(x= interval_bsa)) +
  geom_bar() #+
  # coord_cartesian(ylim=c(0,50))
Treatment %>% 
  ggplot(aes(x= interval_auc)) +
  geom_bar() #+
  # coord_cartesian(ylim=c(0,50))
```

# Variable for filtering

```{r rule between diagnosis and treatment}
Treatment <- Treatment %>% 
  # 1. 60 days rule between diagnosis and treatment # Loss 1
  group_by(patientid) %>% 
  mutate(first_drug_date = first(episodedate)) %>% 
  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
           duration(n=1, units = "days")) %>% 
  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
           duration(n=1, units = "days")) %>% 
  ungroup() %>% 
  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
           duration(n=1, units = "days")
  ) %>% 
  group_by(patientid) %>% 
  mutate(had_carbo_pacli = case_when(
    drugname == "paclitaxel" |
      drugname == "carboplatin"             ~ "Yes"
  )) %>% 
  fill(had_carbo_pacli, .direction = "updown") %>% 
  ungroup() %>% 
  mutate(interval_surgery_to_adj_start = case_when(
      chemotherapy_type == "Adjuvant" &
        linenumber_adj == 1       
      ~ interval(start = surgerydate, end = linestartdate_new) / duration(n = 1, units = "months")
    ),
  )
```

@@

```{r}
rm(areaUC, body_surface_area, creatinine, clinical_data, drugs, drugs1, 
   height#, therapy_cycle, therapy_line, Treatment, weight
   )
```

@@

**We start with a number of `r drugs %>% distinct(patientid) %>% nrow()` patients who received treatment and for who their clinical info are available.**

@@

Are excluded :  
-	Borderline cases (not invasive ovarian cancer)  
-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)  
```{r}
drugs1 <- Frontline_adjusted %>% 
  mutate(flatiron_rules = case_when(
    days_at_first_drug > 90 | 
      days_at_surg > 90                          ~ "exclude",
    thirty_days_exclusion <= 30                  ~ "exclude",
    exclude == "1"                               ~ "exclude"
  )) %>%
  group_by(patientid) %>% 
  fill(flatiron_rules, .direction = "downup")

@@

## 2. step 2: Filter patients with cinical characteristics fitting to the study criteria

- exclude patients whose histology is unknown  
- remove chemotherapy only patients
- include only patients who received platin and/or taxane
```{r}
drugs1 <- drugs1 %>% 
  filter(!is.na(histology)) # loss 287 ################## Will do when bind to drugs
```

```{r}
drugs1 <- drugs1 %>%
  filter(!is.na(surgerydate))
```

```{r}
drugs1 <- drugs1 %>%
  filter(had_carbo_pacli == "Yes")
```

@@

- exclude the patients who had surgery but we don't have a date of surgery -> NONE anymore

```{r}
drugs11 <- drugs1 %>% 
  filter(!(issurgery == "Yes" & is.na(surgerydate))) 
```

- remove patients with long gap between surgery and adjuvant start -> NONE anymore  
Did a 3 months gap
```{r}
drugs11 <- drugs11 %>%
  arrange(patientid, episodedate) %>%
  mutate(ex = case_when(
    interval_surgery_to_adj_start > 3                  ~ "exclude"
  )) %>% 
  filter(is.na(ex))

drugs11 %>% distinct(patientid) %>% nrow()
```

RESTART HERE ----------------------------------------------------

### step 1: Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded)
We have `r drugs1 %>% filter(days_at_first_drug < 0) %>% distinct(patientid) %>% nrow()` patients with date of drug before diagnosis and `r drugs1 %>% filter(days_at_surg < 0) %>% distinct(patientid) %>% nrow()` patients with a date of surgery before diagnosis. Patients left :
```{r}
drugs1 <- drugs1 %>% 
  filter(days_at_first_drug >= 0 &
           (is.na(surgerydate) | days_at_surg >= 0)
         )
drugs1 %>% distinct(patientid) %>% nrow()
```

```{r}
therapy_line <- therapy_line %>% 
  filter(treatment_sequence == "neo + surg + adj" |
           treatment_sequence == "surg + adj")

# Number of patient with a jump line in the first line # 60 would have
# therapy_line %>% 
#   filter(linenumber == 1 & linenumber_new == 2) %>% 
#   arrange(desc(jump_line)) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(jump_line) %>% 
#   tbl_summary()
```

```{r}
therapy_line %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(had_neo, had_adj, therapy) %>% 
  tbl_summary(by = therapy,
              type = list(had_neo ~ "dichotomous", 
                          had_adj ~ "dichotomous"),
              missing = "no")
# therapy_line %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(therapy, treatment_sequence) %>% 
#   tbl_summary(by = therapy)
```

`r emo::ji("check")`

### step 4: Remove linename that doesn't include platinum or taxanes in first line

Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others? `r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev in frontline treatment**</span>    
`r emo::ji("check")`   
```{r}
# F0017FB3A8828 starts with gemcitabine then have carbo

therapy_line <- therapy_line %>%
  # Remove patients with other linename
  filter((linenumber_new == 1 &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin")) |
          (linenumber_new == 2 &
          therapy == "Upfront Chemo" &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Carboplatin"))
         )
```

First table is frontline Neo, second table is frontline Adj.
```{r}
therapy_line %>% 
  filter(linenumber == 1
         ) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

therapy_line %>% 
  filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))
```

We now have `r therapy_line %>% distinct(patientid) %>% nrow()` patients.

### step 5: remove patients with maintenance as first line adjuvant?????
`r emo::ji("question_mark")`
<span style="color:red">**Patients have maintenance as first line Adjuvant then recurrent treatment : Should I remove these patients or keep them for the Neoadjuvant RDI??**</span>
```{r}
therapy_line %>% 
  filter(linenumber_adj == 1) %>% 
  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
  select(ismaintenancetherapy, linename) %>% 
  tbl_summary(by = linename)
# a <- therapy_line %>% 
#   filter(linenumber_adj == 1)
therapy_line %>% 
  filter(linenumber_adj == 1) %>%
  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
  select(ismaintenancetherapy, chemotherapy_type) %>% 
  tbl_summary(by = chemotherapy_type)
therapy_line %>% 
  filter(linenumber_adj == 1, chemotherapy_type == "Neoadjuvant") %>%
  arrange(desc(ismaintenancetherapy)) %>% 
  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
  select(ismaintenancetherapy, chemotherapy_type) %>% 
  tbl_summary(by = chemotherapy_type)
```

#### remove only the maintenance line in neo or adj
```{r remove only the maintenance line in neo or adj}
# therapy_line <- therapy_line %>% 
#   filter(!(ismaintenancetherapy == TRUE & linenumber_adj == 1))
# therapy_line %>% distinct(patientid) %>% nrow()
```

#### OR remove patients with maintenance in neo
```{r remove patients with maintenance in neo}
# remove_neo_patients_maintenance <- therapy_line %>% 
#   filter(linenumber_adj == 1, chemotherapy_type == "Neoadjuvant", ismaintenancetherapy == TRUE) %>%
#   arrange(desc(ismaintenancetherapy)) %>% 
#   distinct(patientid)
# 
# therapy_line <- therapy_line %>%
#   filter(!str_detect(patientid, paste(remove_neo_patients_maintenance$patientid, collapse = "|")))
# therapy_line %>% distinct(patientid) %>% nrow()
```

#### OR remove totally patients with maintenance in frontline neo or adj
```{r remove totally patients with maintenance in neo or adj}
remove_patients_maintenance <- therapy_line %>% 
  filter(linenumber_adj == 1 & ismaintenancetherapy == TRUE) %>%
  arrange(desc(ismaintenancetherapy)) %>% 
  distinct(patientid)

therapy_line <- therapy_line %>%
  filter(!str_detect(patientid, paste(remove_patients_maintenance$patientid, collapse = "|")))
therapy_line %>% distinct(patientid) %>% nrow()
```

#### remove patients with more than 9 cycles total in upfront chemo or upfront surgery

### step 7: Remove patients with more than 1 line as Neo
We are removing the 34 patients who received multiple Neoadjuvant line.   
`r emo::ji("check")`

<!-- Here the lines for the 34 patient. -->
```{r, rows.print = 40}
# therapy_line %>% 
#   filter(chemotherapy_type == "Neoadjuvant" &
#            (linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5)) %>% 
#   select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
#          drugname, episodedate, surgerydate, chemotherapy_type) %>%
#   arrange(patientid, episodedate) %>% 
#   distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
#   select(-linenumber)

remove_morethan1_neo <- therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant" &
           linenumber_new != 1) %>% 
  distinct(patientid)

>>>>

  # 7.Calculate cycle for each line----
  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
  mutate(#drugname_count_perline = n(),
         drugname_count_perline = case_when(
           str_detect(drugname, "carboplatin|paclitaxel")     ~ n()
         )
           ) %>%  # F0000AD999ABF
  ungroup() %>% 
  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor)) %>% 
  group_by(patientid, linenumber_new) %>% 
  mutate(linestartdate_new = min(episodedate)) %>% 
  mutate(lineenddate_new = max(episodedate)) %>% 
  ungroup()
```

```{r cycle coding}
# Code cycle number
therapy_cycle <- therapy_line %>% 
  arrange(patientid, episodedate, drugname) %>% 
  group_by(patientid, linenumber_new) %>%
  # Need the number of time of the "major" drug is seen in the line
  mutate(cycle_count_perline = min(drugname_count_perline, na.rm = TRUE)) %>%
  mutate(cycle_major_drugname = case_when(
    cycle_count_perline == drugname_count_perline &
      (drugname == "carboplatin" |
      drugname == "paclitaxel")                            ~ cycle_drugname,
    TRUE                                                   ~ NA_character_
  )) %>% 
  # select(-drugname_count_perline) %>% 
  group_by(patientid, linenumber_new, cycle_major_drugname) %>%
  mutate(cycle_increment = row_number(cycle_major_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------
  # F01D908A013B7 has more pacli at the end but in the same line

@@

  # group_by(patientid, linenumber_new, cycle_inc) %>%
  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>% 
  arrange(patientid, episodedate, cycle_increment) %>% 
  group_by(patientid, linenumber_new) %>%
  # mutate(cycle_increment = cycle_inc) %>% 
  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
  group_by(patientid, chemotherapy_type, cycle_increment) %>% 
  mutate(is_dose_dense = row_number(cycle_increment),
         is_dose_dense = ifelse(is_dose_dense == 1, 1, NA_real_)) %>% 
  group_by(patientid) %>% 
  mutate(total_cycle_increment = #case_when(
           # ismaintenancetherapy == "FALSE"            ~ 
           row_number(is_dose_dense)
         # )
  ) %>% 
  fill(total_cycle_increment, .direction = "downup") %>% 
  # cycle date
  group_by(patientid, linenumber_new, cycle_increment) %>% 
  mutate(cycle_start_date = min(episodedate)) %>%

@@

  # # CODE FOR SKIPPED CYCLE
  # group_by(patientid, linenumber_new) %>% 
  # mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
  #        cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
  # 
  # # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
  # mutate(n = row_number(drugname)) %>%
  # 
  # mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
  # fill(base_days_between_cycle, .direction = "downup") %>% 
  # mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
  #                                      (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
  # # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
  # group_by(patientid, linenumber_new) %>%
  # mutate(drug_count_perline = n()) %>%
  # mutate(skipped_cycle_indays1 = ifelse(
  #   (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
  # )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
  # # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
  # group_by(patientid) %>% 
  # mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
  # ungroup()

@@

```{r target_auc and expected dose}
Treatment1 <- 
  # Merge with creatinine
  left_join(therapy_cycle, creatinine, by = "patientid") %>%
  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_creat = case_when(
    (therapy == "Upfront Surgery" &
       interval_creat < 31 &
       # creat_date < lineenddate &
       creat_date > surgerydate)                  ~ interval_creat,

@@

```{r plot interval}
# Treatment %>% 
#   ggplot(aes(x= interval_creat)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
# # Treatment %>% 
# #   ggplot(aes(x= interval_height)) +
# #   geom_bar() +
# #   coord_cartesian(ylim=c(0,50))
# Treatment %>% 
#   ggplot(aes(x= interval_weight)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
# Treatment %>% 
#   ggplot(aes(x= interval_bsa)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
# Treatment %>% 
#   ggplot(aes(x= interval_auc)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
```

```{r rule between diagnosis and treatment}
Treatment <- Treatment1 %>% 
  filter(route == "Intravenous") %>% 
  # 1. 60 days rule between diagnosis and treatment # Loss 1
  group_by(patientid) %>% 
  mutate(first_drug_date = first(episodedate)) %>% 
  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
           duration(n=1, units = "days")) %>% 
  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
           duration(n=1, units = "days")) %>% 
  ungroup() %>% 
  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
           duration(n=1, units = "days")
  ) %>% 
  group_by(patientid) %>% 
  mutate(had_carbo_pacli = case_when(
    drugname == "paclitaxel" |
      drugname == "carboplatin"             ~ "Yes"
  )) %>% 
  fill(had_carbo_pacli, .direction = "updown") %>% 
  ungroup() %>% 
  mutate(interval_surgery_to_adj_start = case_when(
      chemotherapy_type == "Adjuvant" &
        linenumber_adj == 1       
      ~ interval(start = surgerydate, end = linestartdate_new) / duration(n = 1, units = "months")
    ),
  ) %>% 
  group_by(patientid) %>% 
  mutate(neo_more_more_than_1line = case_when(
    chemotherapy_type == "Neoadjuvant" &
           linenumber_new != 1                 ~ "exclude"
  )) %>% 
  fill(neo_more_more_than_1line, .direction = "updown") %>% 
  ungroup() %>% 
  mutate(whole_frontline_is_maintenance = case_when(
    (linenumber_new == 1 &
    ismaintenancetherapy == "TRUE") |
    (linenumber_new == 2 &
      therapy == "Upfront Chemo" &
    ismaintenancetherapy == "TRUE")            ~ "exclude"
  )) %>% 
  group_by(patientid) %>% 
  fill(whole_frontline_is_maintenance, .direction = "updown") %>% 
  ungroup() %>% 
  mutate(too_many_cycle = case_when(
    (linenumber_new == 1 &
       therapy == "Upfront Chemo" &
       total_cycle_increment > 6) |

      (linenumber_new == 2 &
         therapy == "Upfront Chemo" &
         total_cycle_increment > 9) |

      (linenumber_new == 1 &
         therapy == "Upfront Surgery" &
         total_cycle_increment > 9)             ~ "exclude"
  )) %>% 
  group_by(patientid) %>%
  fill(too_many_cycle, .direction = "updown") %>%
  ungroup() %>%

  mutate(wrong_pacli_dosedense = case_when(
    drugname == "paclitaxel" &
      is.na(too_many_cycle) &
      (dose_dense == 2 |
      dose_dense > 3) &

      ((linenumber_new == 1 &
       therapy == "Upfront Chemo") |

      (linenumber_new == 2 &
         therapy == "Upfront Chemo") |

      (linenumber_new == 1 &
         therapy == "Upfront Surgery"))
    ~ "exclude"
  )) %>% 
  group_by(patientid) %>%
  fill(wrong_pacli_dosedense, .direction = "updown") %>% 
  ungroup()

  # group_by(patientid, wrong_pacli_dosedense) %>% 
  # mutate(n_dose_dense = n()) %>% 
  # 
  # 
  # 
  # is.na(too_many_cycle)

@@

```{r}
# rm(areaUC, body_surface_area, creatinine, clinical_data, drugs, drugs1, 
#    height#, therapy_cycle, therapy_line, Treatment, weight
#    )
```

@@

@@

Are excluded :  
-	Borderline cases (not invasive ovarian cancer)  
-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)  
```{r}
drugs1 <- Frontline_adjusted %>% 
  mutate(flatiron_rules = case_when(
    days_at_first_drug > 90 | 
      days_at_surg > 90                          ~ "exclude",
    thirty_days_exclusion <= 30                  ~ "exclude",
    exclude == "1"                               ~ "exclude"
  )) %>%
  group_by(patientid) %>% 
  fill(flatiron_rules, .direction = "downup") %>% 
  ungroup()

@@

## 2. step 2: Filter patients with clinical characteristics fitting to the study criteria

- exclude patients whose histology is unknown  
- remove chemotherapy only patients
- include only patients who received platin and/or taxane
- exclude patients who only received neo + surgery
- include patients with single or dual P/T +/- Bev as frontline treatment
```{r}
drugs1 <- drugs1 %>% 
  filter(!is.na(histology)) # loss 287 ################## Will do when bind to drugs

drugs1 <- drugs1 %>%
  filter(!is.na(surgerydate))

drugs1 <- drugs1 %>%
  filter(had_carbo_pacli == "Yes")

drugs1 <- drugs1 %>% 
  filter(treatment_sequence == "neo + surg + adj" |
           treatment_sequence == "surg + adj")

# F0017FB3A8828 starts with gemcitabine then have carbo

drugs1 <- drugs1 %>%
  # Remove patients with other linename
  filter((linenumber_new == 1 &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin")) |
          (linenumber_new == 2 &
          therapy == "Upfront Chemo" &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Carboplatin"))
         )
```

@@

- exclude the patients who had surgery but we don't have a date of surgery -> NONE removed anymore  
- remove patients with long gap between surgery and adjuvant start (3  months) -> NONE removed anymore  
- exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded)
- exclude patients for whose no RDI were available

```{r}
drugs11 <- drugs1 %>% 
  filter(!(issurgery == "Yes" & is.na(surgerydate)))

drugs11 <- drugs11 %>%
  arrange(patientid, episodedate) %>%
  mutate(ex = case_when(
    interval_surgery_to_adj_start > 3                  ~ "exclude"
  )) %>% 
  filter(is.na(ex))

drugs11 <- drugs11 %>% 
  filter(days_at_first_drug >= 0 &
           (is.na(surgerydate) | days_at_surg >= 0)
         )

drugs11 <- drugs11 %>% 
  # remove these patients who switched C > C 
  filter((!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
            !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj) & 
            therapy == "Upfront Chemo") |
           (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj &
            therapy == "Upfront Surgery")))
```
**At the end of the step 3, we have `r drugs11 %>% distinct(patientid) %>% nrow()` patients.**

## 4. step 4: Include patients with treatments following the standart of clinical care

- exclude patients with more than 1 line as Neo
- exclude patients with maintenance within their frontline
- exclude patients with more than 6 cycles in Neo, more than 9 cycles **total** in upfront chemo or more than 9 cycles in upfront surgery
```{r}
drugs111 <- drugs11 %>% 
  # Remove patients with more than 1 line as Neo
  filter(is.na(neo_more_more_than_1line))

drugs111 <- drugs111 %>% 
  filter(is.na(whole_frontline_is_maintenance))

drugs111 <- drugs111 %>% 
  filter(is.na(too_many_cycle))
```
**We have `r drugs111 %>% distinct(patientid) %>% nrow()` patients.**

- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxels
```{r}
Frontline <- drugs111 %>% 
  filter(is.na(wrong_pacli_dosedense))

# drugs111 %>% 
#   mutate(n_dose_dense = factor(n_dose_dense)) %>% 
#   select(n_dose_dense, therapy) %>% 
#   tbl_summary(by = therapy)

test <- Frontline %>% 
  filter(wrong_pacli_dosedense == "exclude")

wrong_pacli_dosedense <- Treatment %>% arrange(patientid, episodedate, drugname) %>% 
  filter(str_detect(patientid, paste(test$patientid, collapse = "|"))) %>% 
  select(patientid, chemotherapy_type, therapy, episodedate, drugname, ismaintenancetherapy, linenumber_new, cycle_increment, too_many_cycle, dose_dense, wrong_pacli_dosedense,  linename)
```
**We have `r Frontline %>% distinct(patientid) %>% nrow()` patients.**

```{r}
# d <- end_patients_Treatment %>% 
#   select(patientid, linename, linenumber_new, chemotherapy_type, therapy, cycle_increment, total_cycle_increment, ismaintenancetherapy)

# end_patients_Treatment %>% 
#   mutate(total_cycle_increment = factor(total_cycle_increment)) %>% 
#   arrange(desc(total_cycle_increment)) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(total_cycle_increment, therapy) %>% 
#   tbl_summary(by = therapy)
```

- exclude patients who switch drug within a line

`r Frontline %>% filter(str_detect(linename, "Car") & drugname == "cisplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line.  
`r Frontline %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line.

<!-- Patients left: -->
```{r}
# switch cispl vs carbo  Car > Cis F1BF7208F0E96

# remove_switch <- therapy_line %>% 
#   filter(linenumber_adj == 1 &
#     ((str_detect(linename, "Carboplatin") & drugname == "cisplatin") |
#   (str_detect(linename, "Cisplatin") & drugname == "carboplatin"))
#   ) %>%
#   distinct(patientid)
# remove_switch <- paste(remove_switch$patientid, collapse = "|")
# 
# therapy_line <- therapy_line %>% 
#   # remove these patients who switched C > C 
#   filter(!str_detect(patientid, remove_switch))
# therapy_line %>% distinct(patientid) %>% nrow()
```

`r Frontline %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.  
<!-- I am removing these patients   -->

<!-- Patients left: -->
```{r}
# remove_switch1 <- therapy_line %>% 
#   filter(
#     str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1
#   ) %>%
#   distinct(patientid)
# remove_switch1 <- paste(remove_switch1$patientid, collapse = "|")
# 
# therapy_line <- therapy_line %>% 
#   # remove these patients who switched C > C 
#   filter(!str_detect(patientid, remove_switch1))
# therapy_line %>% distinct(patientid) %>% nrow()
```

<!-- TABLES -->

```{r}
# drugs11 %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(had_neo, had_adj, therapy) %>% 
#   tbl_summary(by = therapy,
#               type = list(had_neo ~ "dichotomous", 
#                           had_adj ~ "dichotomous"),
#               missing = "no")
# # therapy_line %>% 
# #   distinct(patientid, .keep_all = TRUE) %>% 
# #   select(therapy, treatment_sequence) %>% 
# #   tbl_summary(by = therapy)
```

<!-- First table is frontline Neo, second table is frontline Adj. -->
```{r}
# # drugs1 %>% Need to do in Frontline
#   filter(linenumber == 1
#          ) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(linename) %>% 
#   tbl_summary(sort = list(everything() ~ "frequency"))
# 
# # drugs11 %>% 
# #   filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
# #   distinct(patientid, .keep_all = TRUE) %>% 
# #   select(linename) %>% 
# #   tbl_summary(sort = list(everything() ~ "frequency"))
```

<!-- ### Number of patient who switch line because of surgery from line 1 neoadjuvant to an adjuvant line -->
```{r Number of patient who switch line}
# therapy_line %>% 
#   mutate(change_line = case_when(
#     linenumber == 1 & 
#       linenumber_new == 2 &
#       chemotherapy_type == "Adjuvant" &
#       therapy == "Upfront Chemo"                   ~ 1,
#     TRUE                                           ~ 0
#   )) %>% 
#   arrange(desc(change_line)) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(change_line) %>% 
#   tbl_summary()
```
